We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-01-31 paper/paper.tex
paper

Table \ref{table:observations} and Table \ref{table:simulations}
summarize the mean values and uncertainties for the plane width, $c/a$
ratio and $b/a$ ratio in the observations and simulations, respectively. 
The uncertainty in the observations is computed over the results with
different number of satellites, while in the observations it
corresponds to the standard deviation over different halos. 
In the following subsections we describe in detail the results for the
distributions.

>>>>

Table \ref{table:observations} and Table \ref{table:simulations}
summarize the mean values and uncertainties for the plane $w$, $c/a$
ratio and $b/a$ ratio in the observations and simulations, respectively. 
The uncertainty in the observations is computed over the results with
different number of satellites, while in the simulations it
corresponds to the standard deviation over different halos.

The observed widths are always smaller than its randomized version.
For M31 there is barely a ratio of $0.92$ between observed and
randomized, while for the MW this factor goes down to less than half
$0.48$. 
The observed $c/a$ ratio follows the same extreme trend for
the MW compared to a M31 distribution closer to spherical, 
The $b/a$ ratio is statisically the same between observations and the
spherical randomization.

In the following subsections we describe in detail the results on the 
distributions for $w$, $c/a$ and $b/a$
